---
title: "630HotelOpt"
author: "Marlene Aviles"
date: "5/8/2020"
output:
  pdf_document: default
  html_document: default
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(readr)
library(ggplot2)
library(GGally)
library(caret)
```

## Optimal hotel recommendations for Expedia’s users 

The following analysis will look at data from Expedia's users to recommend an 
optima hotel recommendation.

### Expedia: Test Dataset 
```{r, echo=FALSE, warning=FALSE}
test <- read_csv("~/Desktop/630:640/630 Predictive Analytics/Hotel Optimization Recommendation/test.csv")
#summary(test)
```

### Expedia: Train Dataset
```{r, echo=FALSE, warning=FALSE}
train <- read_csv("~/Desktop/630:640/630 Predictive Analytics/Hotel Optimization Recommendation/train.csv")
#summary(train)
```

### Visuals

```{r, echo=FALSE}
#hist(train$hotel_cluster, train$is_booking)

histogram <- ggplot(train,aes(hotel_cluster)) + geom_histogram(aes(is_booking),stat="count")
histogram + labs(title="Hotel Histogram",y="Booking", x="Hotel Cluster")
```

### Model Creation: Training & Test Sets 

```{r}

inTrain = createDataPartition(y = train$hotel_cluster, # predicting variables 
                              p = 0.7, # proportion of values in training set
                              list = FALSE) # returns vector of indices
 
#Create training and test sets
TrainingSet = data[inTrain, ]
TestSet     = data[-inTrain, ]

```

### Training Model

### Linear Regression
```{r, echo=FALSE}
mod1 = train(y ~ ., 
            data = TrainingSet, 
            method = "glm", 
            family = "binomial")

# Predictions
ptest  = predict(mod, newdata = TestSet)
ptrain = predict(mod, newdata = TrainingSet)
 
# Accuracy
 
# Acc: training set
mean(ptrain == TrainingSet$y)
 
#Acc: Test set
mean(ptest == TestSet$y)
```


### Predictions & Accuracy
```{r}
# Predictions
ptest  = predict(mod, newdata = TestSet)
ptrain = predict(mod, newdata = TrainingSet)
 
# Accuracy
 
# Acc: training set
mean(ptrain == TrainingSet$y)
 
#Acc: Test set
mean(ptest == TestSet$y)
```


### Regression Tree
```{r, echo=FALSE}
mod1 = train(y ~ ., 
            data = TrainingSet, 
            method = "rpart", 
            family = "binomial")

# Predictions
ptest1  = predict(mod1, newdata = TestSet)
ptrain1 = predict(mod1, newdata = TrainingSet)
 
# Accuracy
 
# Acc: training set
mean(ptrain1 == TrainingSet$y)
 
#Acc: Test set
mean(ptest1 == TestSet$y)
```
```

Note that the `echo = FALSE` parameter was added to the code chunk to prevent printing of the R code that generated the plot.
